Evaluation of performances

### 2019-08-19 analysis/eval-performance.Rmd
add new tasks to performance eval report

```{r eval-performance-1}
getBMRAggrPerformances(bm_aggregated, as.df = TRUE) %>%
  mutate(task.id = recode_factor(task.id,
    `defoliation-all-plots-HR` = "HR",
    `defoliation-all-plots-VI` = "VI",
    `defoliation-all-plots-NRI` = "NRI"
  )) %>%
  tidyr::separate(learner.id, c("learner_group", "filter"),
    remove = FALSE,
    sep = " "
  ) %>%
  group_by(learner_group, task.id, filter) %>%
  summarise(best = min(rmse.test.rmse)) %>%
  mutate(filter = replace(filter, is.na(filter), "No Filter")) %>%
  arrange(best) %>%
  knitr::kable()
```

@@

```{r eval-performance-3}
results_aggr <- getBMRAggrPerformances(bm_aggregated, as.df = TRUE) %>%
  mutate(task.id = recode_factor(task.id,
    `defoliation-all-plots-HR` = "HR",
    `defoliation-all-plots-VI` = "VI",
    `defoliation-all-plots-NRI` = "NRI"
  )) %>%
  tidyr::separate(learner.id, c("learner_group"),
    remove = FALSE,
    sep = " "
  ) %>%
  group_by(learner_group, task.id) %>%
  summarise(best = min(rmse.test.rmse))

>>>>

```{r eval-performance-1}
getBMRAggrPerformances(bm_aggregated, as.df = TRUE) %>%
  mutate(task.id = recode_factor(task.id,
    `defoliation-all-plots-HR` = "HR",
    `defoliation-all-plots-VI` = "VI",
    `defoliation-all-plots-NRI` = "NRI",
    `defoliation-all-plots-HR-NRI` = "HR-NRI",
    `defoliation-all-plots-HR-VI` = "HR-VI",
    `defoliation-all-plots-HR-NRI-VI` = "HR-NRI-VI",

  )) %>%
  tidyr::separate(learner.id, c("learner_group", "filter"),
    remove = FALSE,
    sep = " "
  ) %>%
  group_by(learner_group, task.id, filter) %>%
  summarise(best = min(rmse.test.rmse)) %>%
  mutate(filter = replace(filter, is.na(filter), "No Filter")) %>%
  arrange(best) %>%
  knitr::kable()
```

@@

```{r eval-performance-3}
results_aggr <- getBMRAggrPerformances(bm_aggregated, as.df = TRUE) %>%
  mutate(task.id = recode_factor(task.id,
    `defoliation-all-plots-HR` = "HR",
    `defoliation-all-plots-VI` = "VI",
    `defoliation-all-plots-NRI` = "NRI",
    `defoliation-all-plots-HR-NRI` = "HR-NRI",
    `defoliation-all-plots-HR-VI` = "HR-VI",
    `defoliation-all-plots-HR-NRI-VI` = "HR-NRI-VI",
  )) %>%
  tidyr::separate(learner.id, c("learner_group"),
    remove = FALSE,
    sep = " "
  ) %>%
  group_by(learner_group, task.id) %>%
  summarise(best = min(rmse.test.rmse))
